### 2024-04-12 ms.qmd
Updates figures

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for Lampropholis delicata for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_dar_AC_df <- df_plotAC("deli_red")
fig_dar_BD1_df <- df_plotBD1("deli_red")
fig_dar_BD2_df <- df_plotBD2("deli_red")
## Blue
fig_dab_AC_df <- df_plotAC("deli_blue")
fig_dab_BD1_df <- df_plotBD1("deli_blue")
fig_dab_BD2_df <- df_plotBD2("deli_blue")
#
# Second step, create the plots
fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
#
# Third step, merge plots
fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis delicata", size = 6, color = "black", fontface = "italic")
```

@@

```{r, fig-guich}
#| label: fig-guich
#| fig.cap: "Results for Lampropholis guichenoti for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_gar_AC_df <- df_plotAC("guich_red")
fig_gar_BD1_df <- df_plotBD1("guich_red")
fig_gar_BD2_df <- df_plotBD2("guich_red")
## Blue
fig_gab_AC_df <- df_plotAC("guich_blue")
fig_gab_BD1_df <- df_plotBD1("guich_blue")
write.csv(fig_gab_BD1_df, file= "./output/Checking/fig_gab_BD1_df.csv")
fig_gab_BD2_df <- df_plotBD2("guich_blue")
#
# Second step, create the plots
fig_gar <- plotting(sp = "guich", col = "red", df_prob = fig_gar_AC_df, df_violin = fig_gar_BD1_df, df_points = fig_gar_BD2_df)
fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_violin = fig_gab_BD1_df, df_points = fig_gab_BD2_df)
#
# Third step, merge plots
fig_guich <- plot_grid(fig_gar, fig_gab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.25, 1, "cm")) +
  annotate("text", x = 0.5, y = 1.01, label = "Lampropholis guichenoti", size = 6, color = "black", fontface = "italic")
```

>>>>

```{r, fig-deli}
#| label: fig-deli
#| fig.cap: "Results for Lampropholis delicata for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_dar_AC_df <- df_plotAC("deli_red")
fig_dar_BD1_df <- df_plotBD1("deli_red")
fig_dar_BD2_df <- df_plotBD2("deli_red")
## Blue
fig_dab_AC_df <- df_plotAC("deli_blue")
fig_dab_BD1_df <- df_plotBD1("deli_blue")
fig_dab_BD2_df <- df_plotBD2("deli_blue")
#
# Second step, create the plots
fig_dar <- plotting(sp = "deli", col = "red", df_prob = fig_dar_AC_df, df_violin = fig_dar_BD1_df, df_points = fig_dar_BD2_df)
fig_dab <- plotting(sp = "deli", col = "blue", df_prob = fig_dab_AC_df, df_violin = fig_dab_BD1_df, df_points = fig_dab_BD2_df)
#
# Third step, merge plots
fig_deli <- plot_grid(fig_dar, fig_dab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis delicata", size = 4.5, color = "black", fontface = "italic")
ggsave("./output/figures/fig_deli.png", plot=fig_deli, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_deli.png")
```

@@

```{r, fig-guich}
#| label: fig-guich
#| fig.cap: "Results for Lampropholis guichenoti for both colour groups "red" (A,B) and "blue" (C, D). Panels A and C show the predicted probability of choosing the correct feeder first over trials. The lines represent the mean predicted probability of choosing the correct feeder first on each trial, and the shaded areas indicate the standard deviation of the mean; both were obtained by using the slope and intercept estimates from the posterior distributions. The different colours indicate the different treatments. Panels B and D show the distribution of the estimates of slopes per each treatment. The x-axis represents the slope estimate, and in the y-axis are the density of the estimates. The different colours indicate the different treatments. Points and bars represent the mean and standard deviation of the mean of the estimates, respectively."
source(here("R", "func.R"))
# First step, create the dfs for all models
## Red
fig_gar_AC_df <- df_plotAC("guich_red")
fig_gar_BD1_df <- df_plotBD1("guich_red")
fig_gar_BD2_df <- df_plotBD2("guich_red")
## Blue
fig_gab_AC_df <- df_plotAC("guich_blue")
fig_gab_BD1_df <- df_plotBD1("guich_blue")
fig_gab_BD2_df <- df_plotBD2("guich_blue")
#
# Second step, create the plots
fig_gar <- plotting(sp = "guich", col = "red", df_prob = fig_gar_AC_df, df_violin = fig_gar_BD1_df, df_points = fig_gar_BD2_df)
fig_gab <- plotting(sp = "guich", col = "blue", df_prob = fig_gab_AC_df, df_violin = fig_gab_BD1_df, df_points = fig_gab_BD2_df)
#
# Third step, merge plots
fig_guich <- plot_grid(fig_gar, fig_gab, ncol = 1) +
  theme(plot.margin = margin(1, 1, 1.5, 1, "cm")) +
  annotate("text", x = 0.5, y = 0.985, label = "Lampropholis guichenoti", size = 4.5, color = "black", fontface = "italic")
ggsave("./output/figures/fig_guich.png", plot=fig_guich, width = 25, height = 18, units = "cm", dpi = 600)
knitr::include_graphics("./output/figures/fig_guich.png")
```
